Bare Demo of IEEEtran.cls for Journals

### 2019-12-03 2-oracle/report/paper.tex
write network section

@@

\section{Character Recognition}
% wzy
\subsection{Convolutional Neural Network}
% ljy
\subsection{Template Matching}
% ljy
\subsection{Ensemble of Two Methods}

>>>>

\usepackage{CJK}

@@

\section{Character Recognition}
We use two different methods to address the character recognition task for oracle bone characters.
We first learn a deep convolutional neural network to recognize characters, then use the template matching method for the same task.

% wzy
\subsection{Convolutional Neural Network}
The deep neural network for learning the oracle bone characters has the structure in Figure~\ref{fig:network}.

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{fig/network.png}
	\caption{Structure of the DNN}
	\label{fig:network}
\end{figure}

The network first uses 2 convolutional layer with 16 filters, then apply max-pooling and batch normalization, then another 2 convolutional layer with 32 filters and pooling layer with normalization. Lastly, it uses one dense layer and an output layer. All trainable layers except the output layer uses ReLU activation and the output layer uses softmax activation.

We use a simple stochastic gradient descent optimizer to train the network on the 9120 training samples and validate it on the remaining 400 samples.

The network for 10 category classification achieves 98\% accuracy on the validation set at the save point, and the one for 40 category classification achieves 88.5\% accuracy on the validation set at the save point.
Figure~\ref{fig:network-confusion} shows the confusion matrix for the validation results.

\begin{figure}[h]
	\centering
	\begin{minipage}{\linewidth}
		\subfigure[Confusion Matrix for 10 Category Classification]{
			\includegraphics[width=\linewidth]{fig/confusion_oraclenet_conv10.png}
			\label{fig:network-confusion-10}
		}
	\end{minipage}
	\begin{minipage}{\linewidth}
		\hspace{-2em}
		\subfigure[Confusion Matrix for 40 Category Classification]{
			\includegraphics[width=1.15\linewidth]{fig/confusion_oraclenet_conv40.png}
			\label{fig:network-confusion-40}
		}
	\end{minipage}
	\caption{Validation Results}
	\label{fig:network-confusion}
\end{figure}

In Figure~\ref{fig:network-confusion-10}, we can see the classification for 10 macro category is quite accurate, only 7 samples out of 400 is miss-classified.
In Figure~\ref{fig:network-confusion-40}, we use solid lines to separate 10 macro categories among 40 micro categories.
We can see the mistakes made between macro categories is very low and we can use this model for the macro classification task with 98\% accuracy as well.
Most mistakes are made within the macro category.
For example, it miss-classifies many samples for variants of the 3rd and 8th macro categories.

% ljy
\subsection{Template Matching}
% ljy
\subsection{Ensemble of Two Methods}
